%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: classic'
\moderncvcolor{green} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'gray' and 'black'

\usepackage[scale=0.85]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------
\title{}
\firstname{Madeline}
\familyname{Mooney} 

% All information in this block is optional, comment out any lines you don't need
%\title{}
%\address{}{}
\mobile{(585) 363-1526}
\email{m.mooney098@gmail.com}
\homepage{https://www.maddiemooney.github.io}{maddiemooney.github.io}

\quote{New Computer Engineering Graduate seeking Back-End Software Engineering position starting May 2021.}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2016 - 2021}{Rochester Institute of Technology}{}{}{}{Bachelors of Science in Computer Engineering\\
Minor in Computer Science\\
3.35 GPA - Kate Gleason College of Engineering Dean's List}  % Arguments not required can be left empty


%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}
\cventry{Summer 2020}{Vulnerability Research Intern}{Raytheon CODEX}{}{}{Remote Intern on the Cybersecurity Tools and Services team.\\ Optimized Linux build pipeline script execution time by rewriting files from Python to C. }


\smallskip

\cventry{Summer 2019 Fall 2019}{Software Engineering Co-op}{Moog Inc}{}{}{Intern on the IT Solutions team.\\
Designed IoT architecture to gather data from edge devices and alert users using Microsoft Azure resources.\\
Developed test suite for enterprise Java web apps to integrate with Microsoft Azure CI/CD development. }

\smallskip

\cventry{Fall 2018}{Software Engineering Co-op}{Plexus Corp}{}{}{Intern in the Software Group.\\
Implemented integration test structure that utilized DDS protocol to communicate between software items.\\ Validated medical device software as part of FDA approval process.}

\smallskip

\cventry{Summer 2018}{Firmware Engineering Co-op}{AMD}{}{}{Intern on the Diagnostics and Tools team.\\
Automated execution of system level tests and reported test results through web interface.\\ Designed and implemented interface for reserving and offlining test systems.}

\smallskip

\cventry{Fall 2017 Spring 2019}{Teaching Assistant}{Rochester Institute of Technology}{}{}{Head TA for Intro to Computer Engineering, Digital System Design I.\\
Prepared lab exercises, graded lab work and reports, held weekly mentoring meetings and office hours.\\
Recipient of RIT CMPE Fall 2017 Teaching Assistant Award.}

\smallskip

\cventry{Summer 2017}{Machine Learning Research Assistant}{Rochester Institute of Technology}{}{}{Created an online monitoring system that takes sounds produced by different machining processes and labels them according to a classifier created by a support vector machine algorithm.\\
Presented research findings at RIT Undergraduate Research Symposium.}


%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

\cventry{2020}{Hand Washing Monitoring Solution} {}{}{}{Ongoing multidisciplinary project following an engineering design process in order to design a fully tested and documented prototype for potential market.\\
Reminds, monitors, and coaches hospital workers' hand washing process in order to reduce healthcare acquired infections.}

\cventry{2020}{Quarantine Food Storage} {github.com/maddiemooney/QuarantineFoodStorage}{}{}{Monitors grocery decontamination process, and generates alerts for out of stock items.\\
Back-end written in C\#, Android app written in Kotlin.}
    
\smallskip
\cventry{2018}{WriteBot}{github.com/maddiemooney/writebot}{}{}{Repurposing CD drives to create a mini CNC plotting machine. \\
Rewrote the stepper motor library for Arduino, other functionality written in Arduino C and Python.}


%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}

\cvitem{Languages}{C\#, Java, C, ARM/MIPS Assembly, Python, SQL.}
\cvitem{Tools/Misc}{Git, Microsoft Azure Cloud, Agile Development.}

\end{document}